Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-05-22 Manuscript/manuscriptPS.tex
Update simulation details text

  Notation 2$\times$[time] indicates that two independent MD runs was conducted. Additional simulation details are given in the supplementary information.

@@

lipid/counter-ions  & force field for lipids & \footnote{Number of lipid molecules with largest mole fraction}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files & \tabularnewline

@@

  reported in the experiments by Roux et al.~\cite{roux90}.  Notation 2$\times$[time] indicates that two independent MD runs was conducted.

@@

lipid/counter-ions  & force field for lipids / ions  & {[}CaCl$_{2}${]}\,(M)  & \footnote{Number of POPC molecules}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Number of additional cations}N$_{{\rm c}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 120  & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withKCI} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 120 & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withNaCI} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 0.50  & 120 & 5760  & 52  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 1.00  & 120  & 5760  & 104  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 2.00  & 120  & 5760  & 208  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 3.00  & 120 & 5760  & 311  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 4.00  & 120  & 5760  & 415  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 60 & 3600  & 0  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.08  & 60  & 3561  & 5  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.13  & 60  & 3561  & 8  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.20  & 60 & 3561  & 13  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.41  & 60 & 3522  & 26  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.62  & 60 & 3483  & 39  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline

>>>>

  Notation 2$\times$[time] indicates that two independent MD runs was conducted.
  JC refers to the Joung-Cheatham ion parameters~\cite{joung08} and ff99 to the default Amber ion parameters~\cite{aqvist90}.
  Additional simulation details are given in the supplementary information.

@@

lipid/counter-ions  & force field & \footnote{Number of lipid molecules with largest mole fraction}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files & \tabularnewline

@@

  reported in the experiments by Roux et al.~\cite{roux90}.
  Notation 2$\times$[time] indicates that two independent MD runs was conducted.
  Dang refers to the ion parameters by Dang and co-workers~\cite{smith94,dang06}, and ff99 to the default Amber ion parameters~\cite{aqvist90}.

@@

lipid/counter-ions  & force field & {[}CaCl$_{2}${]}\,(M)  & \footnote{Number of POPC molecules}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Number of additional cations}N$_{{\rm c}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120  & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withKCI} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120 & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withNaCI} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0.50  & 120 & 5760  & 52  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 1.00  & 120  & 5760  & 104  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 2.00  & 120  & 5760  & 208  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 3.00  & 120 & 5760  & 311  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 4.00  & 120  & 5760  & 415  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0  & 60 & 3600  & 0  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.08  & 60  & 3561  & 5  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.13  & 60  & 3561  & 8  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.20  & 60 & 3561  & 13  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.41  & 60 & 3522  & 26  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.62  & 60 & 3483  & 39  & 298  & 1050  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
